### 2022-05-18 GB_Simulation_3Species.Rmd
Movement testing script, changes to GB simulation and VAST script

#set lambda at 0 first, change after initial population set
Pop$dem_params$spp1$lambda <- .1
Pop$dem_params$spp2$lambda <- .1
Pop$dem_params$spp3$lambda <- .1

>>>>

#set lambda at 0 first, change after initial population set
Pop$dem_params$spp1$lambda <- .7
Pop$dem_params$spp2$lambda <- .7
Pop$dem_params$spp3$lambda <- .7
